---
title: "How to automate the model analysis?"
author: "Hubert Baniecki"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    number_sections: true
    theme: flatly
    highlight: kate
---

<!-- STYLES FOR modelStudio -->
<style type="text/css">
<!-- .main-container { -->
<!--   max-width: 1200px; -->
<!-- } -->
.r2d3 {
  position: relative !important;
  left: -130px !important;
}

h1 {
  font-size: 24px;
}

h2 {
  font-size: 20px;
}

#user {
  left: -430px !important;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# DALEX

**Load packages.**

```{r warning = FALSE, message = FALSE, results='hide'}
# machine learning
library("DALEX")
library("ranger")

# visualization 
library("patchwork")
library("ggplot2")
```

**Happiness data.**

```{r}
# load data
train <- read.csv("data/happiness_train.csv", row.names = 1)
test <- read.csv("data/happiness_test.csv",  row.names = 1)
knitr::kable(rbind(head(test), tail(test)))
```

**Explain a black-box model.**

```{r}
# fit a model
model_rf <- ranger(score~., data = train)

# create an explainer for the model
explainer_rf <- explain(model_rf,
                        data = test[,-1],
                        y = test$score,
                        colorize = FALSE)
```

```{r fig.height = 8, fig.width = 9}
(plot(model_parts(explainer_rf), subtitle="")) /
  (plot(model_profile(explainer_rf), subtitle="") +
    theme(axis.title.y = element_text(vjust = -40))) +
  plot_layout(heights = c(1, 2))

obs <- test[1,]
pp <- predict_parts(explainer_rf, obs)
pp$label <- rownames(obs)
(plot(pp, subtitle="")) /
  (plot(predict_profile(explainer_rf, obs), subtitle="") +
    theme(axis.title.y = element_text(vjust = -50))) +
  plot_layout(heights = c(1, 2))
```

# modelStudio

Just one line of code...

```{r warning = FALSE, message = FALSE}
library("modelStudio")
modelStudio(explainer_rf,
            options = ms_options(margin_left = 150))
```

## parameters 

Exploring the parameters based on the [vignette](https://modelstudio.drwhy.ai/articles/ms-perks-features.html) and [documentation](https://modelstudio.drwhy.ai/reference/modelStudio.html).

**Observations for local explanations**

```{r eval=FALSE}
new_observation <- test[c('Canada', 'Chile', 'China'), ]

modelStudio(explainer_rf,
            new_observation = new_observation,
            new_observation_y = new_observation$score)

modelStudio(explainer_rf,
            new_observation_n = 10)
```

**Smaller studio**

```{r warning = FALSE, message = FALSE}
modelStudio(explainer_rf,
            facet_dim = c(1, 2),
            options = ms_options(margin_left = 150))
```

**"I have a huge monitor!" **

```{r warning = FALSE, message = FALSE}
modelStudio(explainer_rf,
            facet_dim = c(2, 3),
            widget_id = "user",
            options = ms_options(margin_left = 150))
```

**Longer computation for more accurate results**

```{r eval=FALSE}
modelStudio(explainer_rf,
            N = 300,
            N_fi = 3000,
            B = 15,
            B_fi = 25)
```

## `ms_options`

```{r warning = FALSE, message = FALSE}
modelStudio(explainer_rf,
            max_vars = 4,
            time = 100,
            eda = FALSE,
            options = ms_options(
              margin_left = 150,
              ms_title = "modelStudio on useR!-21",
              ms_subtitle = "https://tinyurl.com/RML2021",
              line_size = 4,
              cp_point_size = 6,
              positive_color = "#ffa58c",
              negative_color = "#ae2c87"
            ))
```

## `ms_update_observations()` &  `ms_update_options()`

```{r warning = FALSE, message = FALSE}
ms <- modelStudio(explainer_rf)
ms_updated <- ms_update_observations(ms, explainer_rf, test[1:3, ])
ms_updated_again <- ms_update_options(ms_updated, facet_dim = c(1, 2), margin_left = 150)
ms_updated_again
```
